% textidote: ignore begin
\section{Large language model implementation}\label{sec:large-language-model-implementation}
% textidote: ignore end

As mentioned in Section~\ref{subsec:must-haves}, some key features, hereby explanations and interactivity, are not
implemented in the first release of the ChessTeacher project.
% textidote: ignore begin % [lt:en:EN_REPEATEDWORDS]
This makes for an application that in the current state may not suffice to resolve the problem statement.
There are several reasons for this gap between our solution and a solution that sufficiently satisfies the problem.
% textidote: ignore end

One reason is, that adding the necessary missing features is rather complex and time-consuming.
As the project has a strict deadline and as the developers are learning the languages and software whilst making the
project, time is somewhat limited.
Prioritizing the features to implement is therefore necessary.
One could argue that the missing features are more vital to the problem than some not as vital implemented features
and should therefore be prioritized higher.
Even though this is true, the reason is that the developers did not have a finished plan for the project at the
beginning of the project and therefore did not have a completed prioritized feature list as a baseline.
Throughout the development process, features are added and removed as the developers' knowledge-base around the topic of
the project improves and grows.
It is therefore difficult to start from a completed features list.
Another argument is that the developers are implementing features chronologically, why some less important features are
implemented before features that has a higher priority.
This approach may not be the most effective in the long term, however, it provides a simpler way to better visualize the
overall progress.

Another reason is, that the developers do not have the experience yet to know how to effectively implement the features.
Even though the process of implementing the core of LLM's is not too complicated, there are a lot of pitfalls that on
the contrary are complicated and are not worth the risk to potentially encounter and having to solve.
An example of a pitfall is that LLM API's most often have a price tag, and often a rather steep one.
It is not straightforward how do deal with limiting the amount of requests made to an LLM API and how to avoid other
common pitfalls, as the developer team is rather new to the field of software engineering and web development
especially.
The potential consequences of overlooked flaws in the code resulting in overdraft or other financial pitfalls is
determined to be too great for it to be worth implementing in the first release of the program.

Therefore, due to the reasons mentioned above LLM implementation is ultimately excluded.
One potential future solution to implement these missing features could be to implement them using proprietary software
such as ChatGPT to generate the feedback based on the Stockfish evaluation.
